Meta-analysis

### 2020-07-27 04_MetaAnalysis.Rmd
add an extra dataset to the export

```{r Save_meta_data, eval=FALSE}
write.csv(slimmer_PM_dat, file = "data/GYmeta_data.csv")
save(dat1, efficacy, PM_mv, YieldContrasts, file = here("cache/Meta-analysisData.Rdata"))
```

>>>>

```{r Save_meta_data, eval=FALSE}
write.csv(slimmer_PM_dat, file = "data/GYmeta_data.csv")
save(dat1, efficacy, slimmer_PM_dat PM_mv, YieldContrasts, file = here("cache/Meta-analysisData.Rdata"))
```
